Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression

### 2022-06-25 docs/rmd/presentation/slides.Rmd
lil progress

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
author: "Roman Hoehn"
affiliation: "Johannes Gutenberg University Mainz"
date: "2022-06-29"
output:
  beamer_presentation:
    #theme: "Darmstadt"
    colortheme: "beaver"
    fonttheme: "structurebold"
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
toc_depth: 1
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

@@

@@

@@

>>>>

---
title: "Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression"
subtitle: "A comparison of epsilon-lexicase Selection and Tournament Selection"
date: "2022-06-29"
output:
  beamer_presentation:
    colortheme: "beaver"
    fonttheme: "structurebold"
    keep_tex: true
    fig_caption: yes
    number_sections: true
    slide_level: 2
toc: yes
toc_depth: 1
bibliography: ../bib/bib/ref.bib
csl: ../bib/csl/harvard1.csl
---

```{r setup, include=FALSE}
library(kableExtra)
library(magrittr)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = "!H")
```

@@

## Research Question

* Does the usage of $\epsilon$-lexicase parent selection influence the generalization behaviour of genetic programming in symbolic regression if compared to tournament selection?

@@

* A metaheuristic that searches for computer programs that solve a given problem
* Evolutionary algorithm that simulates the process of Darwinian evolution:
  1. Fitnessfunction: Evaluates the quality of a solution
  1. Selection: Solutions are selected based on their individual fitness
  2. Variation: Mutation and recombination of solutions
* Unique Features:
  * Evolve solutions of variable length and structure
  * Solutions are typically represented by recursive tree structures

@@

## Motivation

- Generalization

# Theoretical Foundations

@@

## Descriptive Statistics

![Distribution of Errors](../plots/mean_error_boxplot_all.png)

### 2022-06-25 docs/rmd/presentation/slides.tex
lil progress

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usecolortheme{beaver}
\usefonttheme{structurebold}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression},
  pdfauthor={Roman Hoehn},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Analyzing the influence of Selection on Genetic Programming's
Generalization ability in Symbolic Regression}
\subtitle{A comparison of epsilon-lexicase Selection and Tournament
Selection}
\author{Roman Hoehn}
\date{2022-06-29}

@@

\begin{frame}{Introduction}
\ldots{}
\end{frame}

\begin{frame}{Genetic Programming}
\protect\hypertarget{genetic-programming}{}
\ldots{}
\end{frame}

@@

\begin{frame}{Generalization}
\protect\hypertarget{generalization}{}
\ldots{}
\end{frame}

@@

\begin{frame}{Results}
\ldots{}
\end{frame}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usecolortheme{beaver}
\usefonttheme{structurebold}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analyzing the influence of Selection on Genetic Programming's Generalization ability in Symbolic Regression},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{Analyzing the influence of Selection on Genetic Programming's
Generalization ability in Symbolic Regression}
\subtitle{A comparison of epsilon-lexicase Selection and Tournament
Selection}
\author{}
\date{\vspace{-2.5em}2022-06-29}

@@

\begin{frame}{Research Question}
\protect\hypertarget{research-question}{}
\begin{itemize}
\tightlist
\item
  Does the usage of \(\epsilon\)-lexicase parent selection influence the
  generalization behaviour of genetic programming in symbolic regression
  if compared to tournament selection?
\end{itemize}
\end{frame}

\begin{frame}{Genetic Programming}
\protect\hypertarget{genetic-programming}{}
\begin{itemize}
\tightlist
\item
  A metaheuristic that searches for computer programs that solve a given
  problem
\item
  Evolutionary algorithm that simulates the process of Darwinian
  evolution:

  \begin{enumerate}
  \tightlist
  \item
    Fitnessfunction: Evaluates the quality of a solution
  \item
    Selection: Solutions are selected based on their individual fitness
  \item
    Variation: Mutation and recombination of solutions
  \end{enumerate}
\item
  Unique Features:

  \begin{itemize}
  \tightlist
  \item
    Evolve solutions of variable length and structure
  \item
    Solutions are typically represented by recursive tree structures
  \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Generalization}
\protect\hypertarget{generalization}{}
\end{frame}

\begin{frame}{Motivation}
\protect\hypertarget{motivation}{}
\begin{itemize}
\tightlist
\item
  Generalization
\end{itemize}
\end{frame}

\hypertarget{theoretical-foundations}{%
\section{Theoretical Foundations}\label{theoretical-foundations}}

\begin{frame}{Genetic Programming}
\protect\hypertarget{genetic-programming-1}{}
\ldots{}

\ldots{}
\end{frame}

@@

\begin{frame}{Descriptive Statistics}
\protect\hypertarget{descriptive-statistics}{}
\begin{figure}
\centering
\includegraphics{../plots/mean_error_boxplot_all.png}
\caption{Distribution of Errors}
\end{figure}

\ldots{}
\end{frame}
